---
title: "BankMarketing"
group members: "Michael Grogan"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(caret)
library(rpart.plot)
library(MASS)
setwd("~/GitHub/DA6813CaseStudies")
```

## I - Executive Summary
## II - The Problem

The task is to analyze the dataset of customers provided by the banking institution, and determine what combination of personal characteristics and external factors are associated with the highest likelihood of the client subscribing to a term deposit. 

Ascertaining which factors are most correlated with subscribing to term deposits will allow the bank to save time and money by focusing on clients that are likely to subscribe, and avoiding those that are not.

## III - Review of Related Literature
## IV - Methodology

Read data and check for missing values
As is outlined in the case, "duration" serves no predictive purpose, because it can only be known after the call is made, and can't be used in the decision for which customer to call, so it is removed.

The data also needs to be balanced, because with the unmodified dataset, a classifier could achieve 90% accuracy by predicting a 'no' response for every observation.

Upsampling changes y variable name to Class.

First get an idea of most important variables using stepwise feature selection using AIC

The full model doesn't yield more accurate predictions than the step-selected model, so the different models are tested with the limited set of significant predictors.

Test several models (logistic regression, decision tree, random forest, linear SVC) using bootstrapped cross validation to optimize tuning variables



## V - Data

```{r readprepare}
bank<-read.csv('bank-additional.csv',sep=";",stringsAsFactors = T)
sum(is.na(bank))
#duration in column 11
bank<-bank[-11]

#replace month abbreviations with numbers
monthord<-as.character(bank$month)
mn<-c('jan','feb','mar','apr','may','jun','jul',
  'aug','sep','oct','nov','dec')
md<-c(1,2,3,4,5,6,7,8,9,10,11,12)
monthord[monthord %in% mn] <- md[match(monthord, mn)]
bank$month<-as.factor(monthord)

#replace day of week abbreviations with numbers
weekord<-as.character(bank$day_of_week)
mn<-c('mon','tue','wed','thu','fri','sat','sun')
md<-c(1,2,3,4,5,6,7)
weekord[weekord %in% mn] <- md[match(weekord, mn)]
bank$day_of_week<-as.factor(weekord)

#reverse levels so "yes" is returned as the positive class to the caret model
bank$y <- factor(bank$y, levels=rev(levels(bank$y)))

#scale and remove variables with near-zero variance(which turns out to be pdays)
params<-preProcess(bank,method=c("scale","nzv"))
scaledbank<-predict(params,bank)

head(scaledbank)


```
```{r trainsplit}
train<-sample(nrow(scaledbank),0.7*nrow(scaledbank))
banktrain<-scaledbank[train,]
banktest<-scaledbank[-train,]

banktrain<-upSample(x=banktrain[,-ncol(banktrain)],y=banktrain$y)


```


```{r steplog}
fullmodel<-glm(Class~.,banktrain,family=binomial)
stepped<-stepAIC(fullmodel, direction = "both",trace = FALSE)
summary(stepped)
```



```{r plots}
attach(banktrain)
plot(Class,contact,ylab="Contact")
plot(Class,age,ylab="Age")
plot(Class,marital,ylab="Marital Status")
plot(job,Class,xlab="Job")
plot(Class,campaign,ylab="Campaign")
plot(month,Class,xlab="Month")
plot(poutcome,Class,xlab="Outcome")
plot(Class,cons.price.idx,ylab="Price Index")
plot(Class,cons.conf.idx,ylab="Consumer Confidence")
plot(Class,emp.var.rate,ylab="Employment")
detach()
```

```{r}

set.seed(12345)


#TC <- trainControl(method = "boot", number=50,classProbs=TRUE,summaryFunction = twoClassSummary)
TC <- trainControl(method="repeatedcv", number=10, repeats=3)

bankLOG <- train(Class~previous+contact+campaign+cons.price.idx+cons.conf.idx+emp.var.rate+education+day_of_week, data=banktrain,
                 method = "glmnet",
                 metric="Spec",
                 trControl = TC)
bankLOGfull <- train(Class~., data=banktrain,
                 method = "glmnet",
                 metric="Spec",
                 trControl = TC)




predlog<-predict(bankLOG,banktest)

predlogfull<-predict(bankLOGfull,banktest)

print("Selected Model")
confusionMatrix(predlog,banktest$y)

print("Full Model")
confusionMatrix(predlogfull,banktest$y)


```

```{r}

TC <- trainControl(method = "boot", number=50,classProbs=TRUE,summaryFunction = twoClassSummary)
#TC <- trainControl(method="repeatedcv", number=10, repeats=3)

banktree=train(Class~.,data=banktrain, metric="ROC",trControl=TC,method='rpart',control = rpart.control(cp=0.06,minsplit = 15, minbucket = 6))

rpart.plot(banktree$finalModel)


#banktree<-rpart(Class~., data=banktrain, method="class", control=rpart.control(minsplit=15, cp=0.01))
#library(rattle)
#fancyRpartPlot(banktree)

predtree<-predict(banktree,banktest)

confusionMatrix(predtree,banktest$y)

```




```{r}
set.seed(1)


#TC <- trainControl(method = "boot", number=50,classProbs=TRUE,summaryFunction = twoClassSummary)
TC <- trainControl(method="repeatedcv", number=10,repeats=3,
                   classProbs=TRUE,summaryFunction = twoClassSummary)

bankrad <- train(Class~poutcome+job+contact+campaign+month+cons.price.idx+cons.conf.idx+emp.var.rate, data=banktrain,
                 method = "svmLinear",
                 metric="ROC",
                 trControl = TC,
                 tuneGrid = expand.grid(C = seq(0.5, 3, length = 10)))
#)
bankrad

predrad<-predict(bankrad,banktest)


confusionMatrix(predrad,banktest$y)
```



```{r}

set.seed(12345)


TC <- trainControl(method = "boot", number=50,classProbs=TRUE,summaryFunction = twoClassSummary)


bankrf <- train(Class~poutcome+job+loan+contact+campaign+month+cons.price.idx+cons.conf.idx+emp.var.rate+education+day_of_week, data=banktrain,
                 method = "rf",
                 metric="ROC",
                 trControl = TC)
bankrf

predrf<-predict(bankrf,banktest)


confusionMatrix(predrf,banktest$y)
```



## VI - Findings

Logistic regression identifies a slightly higher percentage of "yes" (subscribing to term deposits) clients, but has a lower overall accuracy than the linear SVM. This is because the rate of false "yes" predictions is twice as high for the logistic regression model. The random forest is less accurate than the SVM and has fewer true positives than the logistic regression or SVM. The method

The importance of the false positives in choosing the model depends on the cost of each call compared with the average revenue from a successful call. If that ratio is very large, it will be worth it to sacrifice potential successes in order to avoid wasted calls. 
If each call is very expensive, the decision tree method has the highest accuracy in detecting wasted calls, but it misses more "yes" calls than it accurately predicts.

## VII - Conclusions




```{r}

```

